ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-12-09 proposal.tex
Fixed typo

 \subsection{Steeering Subsystem}
In addition to the block diagram shown in \autoref{fig:steeringmodelarchitecture}, $\theta_r{}_e{}_f$ ref represents the desired steering wheel angle. This desired angle is entered by the user. $\theta$, the actual steering wheel angle, is subtracted from the desired steering wheel angle to find the error between the two positions. This error value is sent to the steering subsystem’s controller. Using this information, the controller generates torque voltages A and B, which are sent to the steering subsystem. New torque voltages are then generated and the actual steering wheel angle is updated.

>>>>

 \subsection{Steering Subsystem}
In addition to the block diagram shown in \autoref{fig:steeringmodelarchitecture}, $\theta_r{}_e{}_f$ ref represents the desired steering wheel angle. This desired angle is entered by the user. $\theta$, the actual steering wheel angle, is subtracted from the desired steering wheel angle to find the error between the two positions. This error value is sent to the steering subsystem’s controller. Using this information, the controller generates torque voltages A and B, which are sent to the steering subsystem. New torque voltages are then generated and the actual steering wheel angle is updated.
